%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% With additional modifications by:
% Alex Conway (alex@ac-media.co.uk)
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

\usepackage{fontspec}

\newfontface\lserif{Arial}

\newcommand{\Csh}{C{\lserif\#}}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Alexander}{Conway}{email alex@ac-media.co.uk{ | tel. 07917428649 }}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{University of Kent}
\descript{BSc in Business Computing}
\location{Graduated July 2012}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Colchester Sixth Form}
\subsection{College}
\descript{4 A Levels}

\location{Graduated July 2008}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{The Gilberd School,}
\subsection{Colchester}
\descript{11 GCSEs}

\location{Graduated July 2006}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Key Modules
%------------------------------------------------

\section{Key Modules / Subjects}

\subsection{Undergraduate}

Introductory \& Further Object Oriented Programming \\
Operating Systems \& Architecture \\
Database Systems \\
Distributed Systems \& Networking \\
Introduction to Intelligent Systems \\
Computer Networks \& Communications \\
{\footnotesize \textit{\textbf{(Final Year Project) }}} \\
Programming teaching tool, featuring an interpreter for a subset of Java

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Over 5000 lines:}
\Csh{} \textbullet{} Java \textbullet{} SQL Server \textbullet{} VB/VB.NET \\
JavaScript \textbullet{} HTML \textbullet{} CSS/LESS \\
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} Python \textbullet{} PostgreSQL \\
\location{Familiar:}
Bash \textbullet{} Powershell \textbullet{} Android \textbullet{} \LaTeX\
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

\section{Profile}
I am an aspiring web developer with a varied background in technology. Over the past couple of years I have gained experience in Microsoft .Net. I'm confident in developing in \Csh{}, ASP.NET, MVC, SQL Server and Entity Framework. I possess good skills on the server side and I'm growing in cofindence with JavaScript, HTML and CSS on the client side.

I have a passion for technology and I am beginning to gain a good level of experience with a wide range of technology. I strive to learn something new from every experience because I believe there is always room for self-improvement both personally and professionally.
\sectionspace % Some whitespace after the section
%------------------------------------------------
% Experience
%------------------------------------------------

\section{Employment}

\runsubsection{Abcam}
\descript{| Software Engineer}

\location{Oct 2015 – Present | Cambridge, Cambridgeshire}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Rebranding project working to tight deadline to implement new branding style.
\item Maintaing and developing features for internal .NET applications \Csh{} MVC 5 SQL Server.
\item Writing unit tests and integration tests. Following test driven development methodology.
\item Maintaining legacy ColdFusion code base and moving functionality to .NET applications.
\item Deploying code to production using using a TeamCity continuous integration pipeline.
\item Working towards implementing a micro-services architecture in preparation for new ERP system.

\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Delphi}
\descript{| IT Engineer + Software Engineer}

\location{Sept 2013 – Present | Sudbury, Suffolk}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Leading a push towards internal web applications developed for Sudbury. Successful port of desktop app to web app already completed. Aiming for more applications to run on web browsers where appropriate. Using ASP.NET MVC and AngularJS technologies.
\item Successful implementation of IIS Web Server to serve internal applications.
\item Writing data analysis software using \Csh{}, contributing to a suite of data visualisation tools. Using WPF and MVVM desgin pattern.
\item Writing bespoke applications for the business primarily in \Csh{} using WPF and MVVM.
\item Leading a move towards virtualisation (VMWare ESXi), now running a number of systems on virtualised hardware.
\item Machine Connectivity, responsible for providing a hardware and software solution to interface with PLCs to output data to SQL Server database.
\item Windows 7 Deployment. Heavily involved in replacing hundreds of devices over two sites. Working to a very tight deadline to ensure seamless transition to new operating system.
\item Direct Material Forecasting System. Ambitious project to provide an integrated cost forecasting system across two sites. Involved integrating two ERP systems QAD and SAP to provide forecasting analysis of material requirements and cost. Using SQL Server stored procedures, SQL Server Reporting Services and \Csh{}.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page
\namesection{Alexander}{Conway}


\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

\section{Personal Information}
\vspace{\topsep}
\begin{tightitemize}
\item Full clean UK driving license
\item Eligible to live and work in the UK
\item References available on request
\end{tightitemize}

\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Employment Cont.
%------------------------------------------------
\section{Employment Cont.}


\runsubsection{Siemens}
\descript{| Software Verification \& Validation}
\location{2013 | Sudbury, Suffolk}
\vspace{\topsep}
\begin{tightitemize}
\item Testing embedded software on medical instruments.
\item Executing manual and automated test plans.
\item Investigating software faults on instruments.
\item Gained excellent knowledge of the software development life cycle.
\item All code was reviewed and thoroughly tested, traceability of requirements right through to testing.
\item Gained knowledge of IBM Rational products, including DOORS requirement management system.
\item Present as the team was transitioning to Agile software engineering practices (Scrum).
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Colchester Institute}
\descript{| Information Systems Administrator}
\location{2012 | Colchester \& Braintree, Essex}
\begin{tightitemize}
\item Assisting team across two sites during the busy enrollment period.
\item Checking accuracy of data held in college systems, querying Oracle databases.
\item Creating Microsoft SSRS Reports from queries on SQL Server and Oracle databases.
\end{tightitemize}
\sectionspace % Some whitespace after the section


\section{Projects / Interests}

\runsubsection{Personal Websites / Development}
\descript{| New Blog}
\location{http://www.alexconway.tech}
\begin{tightitemize}
\item My new personal website, built using Hexo, running on Heroku.
\end{tightitemize}
\descript{| AngularJS Blog}
\begin{tightitemize}
\item My old personal website using NodeJS adn Express on the server and a PostgreSQL database. Client side using AngularJS and modified Bootstrap LESS.
\item The website was self hosted and administered on a cloud VPS instance running CentOS Linux.
\item Currently learning Facebook's React library and Flux design pattern.
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Sport \& Fitness}
\descript{}
\begin{tightitemize}
\item Enjoy keeping fit, working out at the gym.
\item Enjoy running and have recently taken up cycling.
\item Interested in nutrition eating healthy and cooking nutritious food.
\end{tightitemize}
\sectionspace % Some whitespace after the section


\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
